% !TEX root = resume.tex

\section{Experience}
\resumeSubHeadingListStart
\resumeSubheading
{Software Developer Intern}{Toronto, Ontario}
{Lynkr Inc}{Sep. 2025 -- Dec. 2025}
\resumeItemListStart
\resumeItem{Co-led the development of \textbf{Lynkr Workbench}, the flagship product, from inception to beta, generating over \textbf{\$100,000 CAD} in revenue.}
\resumeItem{Built a containerized \textbf{FastAPI + Next.js} solution using Docker, featuring an AI orchestration pipeline to manage agent creation and execution.}
\resumeItem{Improved deployment efficiency on \textbf{GKE} by migrating the database seeder to a dedicated \textbf{Kubernetes Job}, eliminating health check failures and reducing application startup time by \textbf{40\%}.}
\resumeItem{Architected \textbf{multi-organization support} with tenant isolation and RBAC (role-based access control), enabling secure data segregation and independent configuration per organization.}
\resumeItem{Integrated \textbf{multi-factor authentication (MFA)} using TOTP (Time-based One-Time Password) and SMS verification via \textbf{Twilio}, significantly enhancing account security and reducing unauthorized access risks.}
\resumeItem{Developed a comprehensive \textbf{audit logging system} to track all user actions, administrative changes, and security events, ensuring compliance with regulatory requirements.}
\resumeItem{Implemented \textbf{session invalidation mechanisms} using JWT (JSON Web Tokens), including logout functionality, idle timeout detection, and remote session termination for enhanced security.}
\resumeItemListEnd

\resumeSubheading
{WE Accelerate Program - Azure and Artificial Intelligence}{Waterloo, Ontario}
{University of Waterloo}{Jan. 2025 -- Apr. 2025}
\resumeItemListStart
\resumeItem{Led a team of 5 in the \textbf{WE Accelerate Program} to design an AI-based solution preventing financial fraud against elders.}
\resumeItem{Developed a comprehensive project planning tool and pipeline sequence wireframe, visualizing each step and aligning deliverables with industry best practices.}
\resumeItem{Collaborated closely with a project mentor to refine goals, validate assumptions, and incorporate \textbf{real-world AI considerations} into the solution.}
\resumeItemListEnd

\resumeSubHeadingListEnd
